---
title: "exc day 4: Isotope Calculation"
author: Manuel, Niklas, Eva
output: html_notebook
---

# 1. Create a model in which the ammonium pool is supplied by Mineralization of SOM.
**Ammonium is subsequently nitrified to nitrate. During the process, N2O is released from the system (range between 0.1 and 10%). Finally, nitrate is taken up by a sink pool representing for example plant uptake and denitrification. Also in this step, small amounts of N2O are released (range 1 to 10%). Select the appropriate model among the Threep... models.**

We choose the ThreepSeriesModel() because the three pools are linked in series
and there is no feedback between the different pools.

```{r}


```

2. Use k-rates of 0.8, 0.7, 0.09 and assume mineralization of 10 units at a delta value of 5per mil to run the model for 100 years at monthly resolution. Explain the results (use getC(model) and getReleaseFlux(model))
```{r}

```


3. Based on the model output, calculate the isotopic delta value for ammonium (use a fractionation factor of ğœ€=-20) according to the closed system Rayleigh equation ğ›¿ğ‘ ğ‘¢ğ‘ğ‘ ğ‘¡ğ‘Ÿğ‘ğ‘¡=ğ›¿ğ‘ ğ‘¢ğ‘ğ‘ ğ‘¡ğ‘Ÿğ‘ğ‘¡,0+ğœ€ ln (ğ‘“) . The lecture material tells you about the residual fraction f.
```{r}

```

4. Show if the delta value of ammonium a sensitive parameter for the amount of N2O produced during nitrification. Dont forget to consider mixing!

```{r}

```

