---
title: "exc day 4: Isotope Calculation"
author: Manuel, Niklas, Eva
output: html_notebook
---

# 1. Create a model in which the ammonium pool is supplied by Mineralization of SOM.
**Ammonium is subsequently nitrified to nitrate. During the process, N2O is released from the system (range between 0.1 and 10%). Finally, nitrate is taken up by a sink pool representing for example plant uptake and denitrification. Also in this step, small amounts of N2O are released (range 1 to 10%). Select the appropriate model among the Threep... models.**

We choose the ThreepSeriesModel() because the three pools are linked in series
and there is no feedback between the different pools.

```{r}


```

2. Use k-rates of 0.8, 0.7, 0.09 and assume mineralization of 10 units at a delta value of 5per mil to run the model for 100 years at monthly resolution. Explain the results (use getC(model) and getReleaseFlux(model))

In the beginning, the Ammonium pool is biggest, than the Nitrate pool and the plant sink is smallest. After a while, nitrification makes nitrate from the ammonium and the nitrate pool becomes bigger. But not a lot because the nitrate is stored in the plant sink. Eventually the system reaches a balanced state where the plant sink is biggest. 
The release flux of ammonium is higher than that of nitrate becuse the decomposition rate of ammonium is bigger. Because we took two times a transfer % of 95% an NO2 release of 5% (instead of 0.1-10% and 1-10%), we can compare the release fluxes based on the decomposition rate. 
```{r}

```


3. Based on the model output, calculate the isotopic delta value for ammonium (use a fractionation factor of ğœ€=-20) according to the closed system Rayleigh equation ğ›¿ğ‘ ğ‘¢ğ‘ğ‘ ğ‘¡ğ‘Ÿğ‘ğ‘¡=ğ›¿ğ‘ ğ‘¢ğ‘ğ‘ ğ‘¡ğ‘Ÿğ‘ğ‘¡,0+ğœ€ ln (ğ‘“) . The lecture material tells you about the residual fraction f.
```{r}

```

4. Show if the delta value of ammonium a sensitive parameter for the amount of N2O produced during nitrification. Dont forget to consider mixing!

```{r}

```

